|

### 2022-09-08 paper/paper.Rmd
Video links added.

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/proj1_rf.png}
\includegraphics[width=0.32\textwidth]{figures/proj1_lda.png}
\includegraphics[width=0.32\textwidth]{figures/proj1_data.png}}
\caption{Projection identified using the manual tour, because it reveals an interesting structure in the predictions from the RF model (left). We can clearly see a block structure, while the LDA model (middle) produces linear boundaries. The three groups are nicely separated in this projection of the data (right)}.
\label{proj1}
\end{figure*}

XXXX currently in the notebook $A_1$ is called A5, and $A_2$ is called A6

@@

>>>>

@@

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/proj1_rf.png}
\includegraphics[width=0.32\textwidth]{figures/proj1_lda.png}
\includegraphics[width=0.32\textwidth]{figures/proj1_data.png}}
\caption{Projection identified using the manual tour, because it reveals an interesting structure in the predictions from the RF model (left). We can clearly see a block structure, while the LDA model (middle) produces linear boundaries. The three groups are nicely separated in this projection of the data (right).}
\label{proj1}
\end{figure*}

This example can be reproduced with the code in penguins_exploring_manually.nb and a run through is shown in the video at https://vimeo.com/747585410.

This example can be reproduced with the code in penguins_slicing_through_center.nb and a run through is shown in the first part of the video at https://vimeo.com/747590472.

This example can be reproduced with the code in penguins_shifting_slice_center.nb and a run through is shown in the second part of the video at https://vimeo.com/747590472.
